An Imaging Search for Circumstellar Companions of Sirius B

### 2021-08-13 paper/paper.tex
update paper with grammarly

The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983}. They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. The IR excess would be indicative of thermal emission of faint material around the star, such as a circumstellar disk or giant planet. They studied $\sim$100 white dwarfs but found no companions. The same method was applied by \citet{zuckerman_excess_1987}, who found excess IR emission around white dwarf G29-38. The emission was determined to be from a dust disk \citep{telesco_observations_1990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koester_metals_1997}. It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsor_pollution_2015}. \citet{skemer_sirius_2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust therefore suppressing any IR excess.

@@

A particularly fascinating such target is Sirius B, the closest and brightest white dwarf. The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,gaia_collaboration_gaia_2018}. As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging. Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortney_giant_2010}.

@@

To find the total age of Sirius B, \citet{bond_sirius_2017} used isochrones to constrain the cooling age (\qty{126}{\mega\year}), first. Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bond_sirius_2017}. An age uncertainty of $\sim$1\% is execeptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.

@@

In this work we report direct images of Sirius B with Keck/NIRC2. The rest of the manuscript is organized as follows: \cref{sec:obs} describes our target and observing strategy, \cref{sec:analysis} describes the processing and analysis techniques used, and \cref{sec:results} describes our results.

@@

During each observation, we took dark frames and sky flat frames for calibration. All observations were taken with the telescope's field rotator set to track the telescope pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{marois_angular_2006}.

@@

The raw images from NIRC2 required pre-processing before analyzing them for companions. For each epoch we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We removed sky background using a high-pass median filter with a box size of 31 pixels. For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter. At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \cref{fig:spike}. Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.

@@

\begin{figure*}
    \centering
    \epsscale{0.95}
    \plotone{sig}
    \caption{The \textit{significance} maps for each epoch accounting for small sample statistics \citep{mawet_fundamental_2014}. Typically a critical value for detection is 5. The inner full-width at half-maximum (FWHM) is masked out for each map.}
    \label{fig:sig}
\end{figure*}

\begin{figure*}
    \centering
    \epsscale{0.95}
    \plotone{stim}
    \caption{The STIM maps for each epoch calculated from the residual cube. The STIM probability has a typical cutoff threshold of 0.5 for significant detections. The inner full-width at half-maximum (FWHM) is masked out for each map.}
    \label{fig:stim}
\end{figure*}

By taking data with the field rotator disabled (ADI), the point-spread function (PSF) will not appear to rotate while any potential companion will appear to rotate. This reduces the probability of subtracting companion signal when we subtract the stellar PSF model. After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottom_noise-weighted_2017}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.

For this analysis we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}. The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames which have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.

@@

A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components). For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10. We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\cref{fig:pca-contrast-curves}). In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic. The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map. A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components. The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \cref{sec:adi-results}.

@@

We determined the best-performing algorithms for each epoch using the contrast curves described in \cref{sec:analysis}. For the first two epochs full-frame median subtraction had the best contrast at almost all separations. For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}. The innermost annulus from this algorithm has invalid contrast (\textgreater1) and is not shown. The collapsed residual frames from each epoch are shown in \cref{fig:residuals}, along with the Gaussian significance maps (\cref{fig:sig}) and STIM maps (\cref{fig:stim}).

@@

It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF. Both of these algorithms usually outperform traditional median and PCA subtraction for disk imaging. In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen which is similar to other disk images \citep[e.g., fig.~7][]{norris_vampires_2014}. Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess. Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/ZIMPOL) may be able to image such a disk.

The contrast maps from the best performing algorithm for each reduction are shown in \cref{fig:contrast}. We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}). Then we use an age of \qty{225}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}. The high precision of the Sirius system's age (see \cref{sec:intro}) reduces uncertainty when interpolating planetary mass from the evolutionary grids. We also tested using the newer SONORA grid \citep{marley_mark_2018_1309035,marley_sonora_2021}, but the differences compared to AMES-Cond were less than the mean uncertainty from age. The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the background limited regime.

@@

In closing, the Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR. While it is highly unlikely a first-generation planet survived post-MS evolution, imaging efforts have gradually increased the sensitivity to second-generation planets. In this work we present high-contrast images of Sirius B in the near-IR. Our sensitivity limits are the best that have been reached for Sirius B so far, reaching \qty{0.6}{\jupitermass} at \qty{1.5}{\au}, the outer limit for dynamically stable orbits. Our observations also show how the high precision of the parameters of the Sirius system directly benefit the sensitivity to planets. Particularly, the low age uncertainty of Sirius B keeps our mass uncertainty below \qty{0.1}{\jupitermass}. Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results. This non-detection furthers evidence against a second-generation planet migrating or forming within the Sirius system \citep{vigan_high-contrast_2015}.

For future work, we consider two potential improvements on our observations. As mentioned in \cref{sec:results}, optical observations using an instrument like Subaru/VAMPIRES \citep{norris_vampires_2014} or VLT/ZIMPOL \citep{schmid_zimpol_2018}. Optical observations can look for disks in the Rayleigh-scattering regime, which is not readily probed by IR observations. Furthermore, the polarimetric differential observation modes of both instruments allow for nearly diffraction-limited imaging, down to 10s of milliarcseconds.

Followup in the IR from space-based telescopes would increase the sensitivity of the observations due to the absence of background emission from Earth's atmosphere. For example, using JWST/NIRCAM in long wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at \textgreater\ang{;;0.3} without saturation \citep{pontoppidan_pandeia_2016}. The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) would still probe down to \qty{0.8}{\au}. Observations would be complicated by the scattered light from Sirius A, which could affect the fine-pointing control or worsen the background sensitivity. In the end, our ground-based observations are already quite close to the atmospheric model grid limits, raising the concern of diminishing returns. Planetary atmosphere models must improve, before fully reaping the benefits of the additional sensitivity of space-based observations.

@@

\begin{acknowledgements}
The data presented herein were obtained at the W. M. Keck Observatory, which is operated as a scientific partnership among the California Institute of Technology, the University of California and the National Aeronautics and Space Administration. The Observatory was made possible by the generous financial support of the W. M. Keck Foundation. The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Maunakea has always had within the indigenous Hawaiian community. We are most fortunate to have the opportunity to conduct observations from this mountain.
\end{acknowledgements}

@@

We found multiple interesting blobs in the reduced data that were not statistically significant. Nonetheless, we tried fitting Keplerian orbits using OFTI to determine the feasibility of the blobs being real companions. We began by estimating the astrometry of the blobs by eye in reduced data (\cref{tbl:astrometry}, \cref{fig:prov-orbit}). We tried simulating $10^4$ orbits via rejection sampling with OFTI but failed to constrain all three points with any one orbit. Overall we determine these blobs are not real companions and are most likely systematic noise in the stellar PSF.

@@

\begin{figure}[h!]
    \centering
    \figurenum{13}
    \plotone{orbit_frames}
    \caption{Provisional astrometry (white circles) displayed on collapsed and derotated residuals from each epoch. Each frame was cropped to the inner $\sim$\qty{7}{\au} (\ang{;;0.25}) and the inner FWHM has been masked out. The width of the circles represent the uncertainty.}
    \label{fig:prov-orbit}
\end{figure}

>>>>

The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983}. They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. The IR excess would be indicative of thermal emission of faint material around the star, such as a circumstellar disk or giant planet. They studied $\sim$100 white dwarfs but found no companions. The same method was applied by \citet{zuckerman_excess_1987}, who found excess IR emission around white dwarf G29-38. The emission was determined to be from a dust disk \citep{telesco_observations_1990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koester_metals_1997}. It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsor_pollution_2015}. \citet{skemer_sirius_2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.

@@

A particularly fascinating target is Sirius B, the closest and brightest white dwarf. The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,gaia_collaboration_gaia_2018}. As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging. Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortney_giant_2010}.

@@

To find the total age of Sirius B, \citet{bond_sirius_2017} used isochrones to constrain the cooling age (\qty{126}{\mega\year}), first. Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bond_sirius_2017}. An age uncertainty of $\sim$1\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.

@@

In this work, we report direct images of Sirius B with Keck/NIRC2. The rest of the manuscript is organized as follows: \cref{sec:obs} describes our target and observing strategy, \cref{sec:analysis} describes the processing and analysis techniques used, and \cref{sec:results} describes our results.

@@

During each observation, we took dark frames and sky-flat frames for calibration. All observations were taken with the telescope's field rotator set to track the telescope pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{marois_angular_2006}.

@@

The raw images from NIRC2 required pre-processing before analyzing them for companions. For each epoch, we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We removed sky background using a high-pass median filter with a box size of 31 pixels. For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter. At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \cref{fig:spike}. Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.

@@

\begin{figure*}
    \centering
    \epsscale{0.95}
    \plotone{sig}
    \caption{The \textit{significance} maps for each epoch accounting for small-sample statistics \citep{mawet_fundamental_2014}. Typically a critical value for detection is 5. The inner full-width at half-maximum (FWHM) is masked out for each map.}
    \label{fig:sig}
\end{figure*}

\begin{figure*}
    \centering
    \epsscale{0.95}
    \plotone{stim}
    \caption{The STIM maps for each epoch calculated from each residual cube. The STIM probability has a typical cutoff threshold of 0.5 for significant detections. The inner full-width at half-maximum (FWHM) is masked out for each map.}
    \label{fig:stim}
\end{figure*}

By taking data with the field rotator disabled (ADI), the point-spread function (PSF) will not appear to rotate while any potential companion will appear to rotate. This reduces the probability of removing companion signal when we subtract the stellar PSF model. After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottom_noise-weighted_2017}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.

For this analysis, we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}. The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.

@@

A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components). For PCA, NMF, and GreeDS algorithms, we increased the number of components from 1 to 10, creating a residual cube for each iteration. We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\cref{fig:pca-contrast-curves}). In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic. The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map. A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components. The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \cref{sec:adi-results}.

@@

We determined the best-performing algorithms for each epoch using the contrast curves described in \cref{sec:analysis}. For the first two epochs, full-frame median subtraction had the best contrast at almost all separations. For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}. The innermost annulus from this algorithm has invalid contrast (\textgreater1) and is not shown. The collapsed residual frames from each epoch are shown in \cref{fig:residuals}, along with the Gaussian significance maps (\cref{fig:sig}) and STIM maps (\cref{fig:stim}).

@@

It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF. Both of these algorithms usually outperform traditional median and PCA subtraction for disk imaging. In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen which is similar to other disk images \citep[e.g., fig.~7][]{norris_vampires_2014}. Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition, there is no prior evidence for a circumstellar disk from IR excess. Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/ZIMPOL) may be able to image such a disk.

The contrast maps from the best performing algorithm for each reduction are shown in \cref{fig:contrast}. We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}). Then we used \qty{225}{\mega\year} for the system age to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}. The high precision of the Sirius system's age reduces uncertainty when interpolating planetary mass from the evolutionary grids (see \cref{sec:intro}). We also tested using the newer SONORA grid \citep{marley_mark_2018_1309035,marley_sonora_2021}, but the differences compared to AMES-Cond were less than the mean uncertainty from age. The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the background limited regime.

@@

In closing, the Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR. While it is highly unlikely a first-generation planet survived post-MS evolution, imaging efforts have gradually increased the sensitivity to second-generation planets. In this work, we present high-contrast images of Sirius B in the near-IR. Our sensitivity limits are the best that have been reached for Sirius B so far, reaching \qty{0.6}{\jupitermass} at \qty{1.5}{\au}, the outer limit for dynamically stable orbits. Our observations also show how the high precision of the parameters of the Sirius system directly benefits the sensitivity to planets. Particularly, the low age uncertainty of Sirius B keeps our mass uncertainty below \qty{0.1}{\jupitermass}. Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results. This non-detection furthers evidence against a second-generation planet migrating or forming within the Sirius system \citep{vigan_high-contrast_2015}.

For future work, we consider two avenues for followup. As mentioned in \cref{sec:results}, optical observations using an instrument like Subaru/VAMPIRES \citep{norris_vampires_2014} or VLT/ZIMPOL \citep{schmid_zimpol_2018}. Optical observations can look for disks in the Rayleigh-scattering regime, which is not readily probed by IR observations. Furthermore, the polarimetric differential observation modes of both instruments allow for nearly diffraction-limited imaging, down to 10s of milliarcseconds.

Followup in the IR from space-based telescopes would increase the sensitivity of the observations due to the absence of background emission from Earth's atmosphere. For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at \textgreater\ang{;;0.3} without saturation \citep{pontoppidan_pandeia_2016}. The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) would still probe down to \qty{0.8}{\au}. Observations would be complicated by the scattered light from Sirius A, which could affect the fine-pointing control or worsen the background sensitivity. In the end, our ground-based observations are already quite close to the atmospheric model grid limits, raising the concern of diminishing returns. Planetary atmosphere models must improve, before fully reaping the benefits of the additional sensitivity of space-based observations.

@@

\begin{acknowledgements}
The data presented herein were obtained at the W. M. Keck Observatory, which is operated as a scientific partnership among the California Institute of Technology, the University of California, and the National Aeronautics and Space Administration. The Observatory was made possible by the generous financial support of the W. M. Keck Foundation. The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Maunakea has always had within the indigenous Hawaiian community. We are most fortunate to have the opportunity to conduct observations from this mountain.
\end{acknowledgements}

@@

We found multiple interesting blobs in the reduced data that were not statistically significant. Nonetheless, we tried fitting Keplerian orbits using OFTI to determine the feasibility of the blobs being real companions. We began by estimating the astrometry of the blobs by eye in reduced data (\cref{tbl:astrometry}, \cref{fig:prov-orbit}). We tried simulating $10^4$ orbits via rejection sampling with OFTI but no generated orbit was able to constrain all three points. Overall we determine these blobs are not real companions and are most likely systematic noise in the stellar PSF.

@@

\begin{figure}[h!]
    \centering
    \figurenum{13}
    \plotone{orbit_frames}
    \caption{Provisional astrometry (white circles) displayed on collapsed and derotated residuals from each epoch. Each frame was cropped to the inner $\sim$\qty{7}{\au} (\ang{;;0.25}) and the inner FWHM has been masked out. The width of the circles represents the uncertainty.}
    \label{fig:prov-orbit}
\end{figure}
